\section{Stakeholder Concerns}

In this project there are four different stakeholder :
\begin{enumerate}
\item The Initiator
\item AirFrance - KLM
\item The Dutch Government
\item EU Claim
\end{enumerate}

Each of them had different concerns within this project which are stated in the next subsections.

\subsection{Initiator}
The initiator is the one who started this project. He wants FlyWithUs to be a success and become the number one rating site people will go to. He want to be able to collect data from social media, other rating websites, news, weather and every other source that can be of importance. This data an then be used to provide the airlines with powerfull statistics and can give users a final rating. Users that make use of FlyWithUs have to be able to post reviews and ratings on the website and search for them. What makes FlyWithUs unique is the fact that airlines can get in touch with the users by sending them messages.

\subsection{AirFrance - KLM}
This stakeholder wants to have a reporting tool. With the tool he has to be able to see what recent reviews have been posted about his airline. Also, AirFrance - KLM wants to see statistics and be able to see what causes a sudden decline or increase in the rating. Furthermore, AirFrance-KLM wants to be able to enter flight information and by doing so influence the weight of review. This means that the weight of a rating has to be less when bad ratings are due to for example environmental issues (bad weather etc.) and have nothing to do with the airline companies services.

\subsection{Dutch Government}
Privacy is an important issue for the Dutch Government. The server needs to be hosted in the Netherlands so FlyWithUs will be led according to the Dutch Privacy Law. Also, the Dutch Governemnt would like to see the project to be a "Green IT" project. 

\subsection{EU Claim}
EU Claim wants to make certain that the privacy if the user is guaranteed. Furthermore the airlines have to behave on the website and do not mess with the results or bribe the users. Fairness is thus also an important issue to this stakeholder.