\documentclass{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{hyperref}

\renewcommand{\arraystretch}{1.5}
\begin{document}
\title{Architecture Documentation Review}
\author{Chiel Peters, Omar Pakker, Mary Gouseti, Cindy Berghuizen}
\maketitle
\setlength\parindent{0pt}
\newcommand{\blank}[1]{\hspace*{#1}}

\section{Introduction}

In this document the architectural solution of the FlyWithUs airline reputation management system is reviewed. The review uses question sets and scenario analysis to determine the completeness
of the architecture. Section two reviews the architecture using premade question sets from \cite{tyree}. In section three multiple scenario's are analysed and how the architecture responds/copes with those scenario's. 

\section{Question sets}

This section contains the answers to the question sets defined in \cite{tyree}. Two question sets where mandatory for this review and the last was specifically taken in order to explain certain limitations in the current version of
the architecture. The first subsection contains questions related to stakeholders and their concerns. In the second subsection the requirements and key design decisions are discussed. Third and final, the viewpoints in the architecture
are reviewed.

\subsection{Question set : Capturing the right stakeholders and concerns}
\input{StakeholderQuestions}

\newpage
\subsection{Question set : Identify architecturally significant requirements and key design decisions}
\input{ArchitectureQuestions}

\newpage
\subsection{Question set : Reviewing the choice of Viewpoints}
\newpage
\input{Scenarios}

\begin{thebibliography}{9}
\bibitem{clemens}
Bass et al.
  \emph{Software Architecture in Practice}.
  Addison Wesley, Boston,
  3rd Edition,
  2012.
\bibitem{tyree}
Tyree, J.  Akerman, A. 
\emph{Architecture Decisions:
Demystifying Architecture},
IEEE Software,
2005

\end{thebibliography}

\end{document}
